Data irregularities across six implicit learning articles: Comments on Lola and Tzetzis (2021), Lola, Giatis, Pérez-Turpin, and Tzetzis (In Press), Lola and Tzetzis (2020), Tzetzis and Lola (2015), Lola, Tzetzis, and Zetou (2012), and Tzetzis and Lola (2010)

### 2021-09-29 docs/manuscript/manuscript.tex
fix: spacing issues on title page and location of Table 1

@@

\addORCIDlink{Brad McKay}{0000-0002-7408-2323}

\addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}

>>>>

\note{

\vspace{\baselineskip}

\raggedright Submitted to \emph{Meta-Psychology}. Participate in open peer review by commenting through hypothes.is directly on this preprint. The full editorial process of all articles under review at \emph{Meta-Psychology} can be found here: \url{https://tinyurl.com/mp-submissions} You will find this preprint by searching for the first author's name.

@@

\vspace{-4em} 
\addORCIDlink{Brad McKay}{0000-0002-7408-2323}  
\newline \indent \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
